Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2018-09-04 Response.tex

        However, the example in Section 4.2 illustrates that the proposed approach can be linked together to compute low-thrust transfers for more challenging maneuvers, with the requirement of correcting energy error at the last stage. 
        This example demonstrates a possible approach to linking several computations of the reachability set to achieve a larger and more challenging transfer.
        There is still a difference in Jacobi energy which is corrected in the final stage.
        If needed in the multi stage examples, the Jacobi energy can be corrected in the intermediate steps to reduce the energy gap in the last stage.

        This paper is motivated by the current common practice of computing low thrust orbital transfers, where a large set of initial guess is repeatedly optimized in a computationally intensive manner. 
        The main contribution is presenting an alternative framework of constructing low thrust orbital transfers in a more efficient and systematic fashion. 
        The example in Section 4.2 demonstrates the use of several intersections of the reachability set to determine a transfer.

        In the revised manuscript, the following paragraph is added in Section 4.2 to explicitly describe the requirement of energy correction at the last stage, its implication and potential difficulties.

        \begin{correction}
            This numerical example demonstrates the ability to link several computations of the reachability set to enable a more general transfer.
            We use eight iterations of computing the reachability set in order to transfer from the geostationary orbit to the stable manifold.
            The example shows a transfer between an initial geostationary orbit and the stable manifold associated with a periodic orbit. 
            This approach allows for a larger class of potential transfers which leverage the capabilities of low-thrust propulsion systems.
            However, the presented approach does not offer a optimal solution in terms of energy/fuel usage. 
            The reachability sets are computed on the lower dimensional \Poincare section.
            As a result, the repeated intersections of the trajectory with the \Poincare section results in a fuel inefficient transfer.
            Furthermore, the issue of discrepancy in the Jacobi integral may become more serious when multiple reachability sets are interconnected. 
            Nonetheless, we are able to apply the proposed approach for the challenging case where the reachability set is not sufficiently close to the invariant manifold to the target orbit. 
            Consequently, this example illustrates a straightforward method to depart from the natural dynamics and transfer to a large region of the phase space that is not accessible via invariant manifolds alone.
            The presented idea of connecting reachability sets can be further studied to address the aforementioned issues of optimality and mismatch of the Jacobi integral.
        \end{correction}

@@

    \item
        \begin{itshape}

            Given the significant remaining issues above, I am going to keep further
            feedback a bit more brief:

            * As mentioned before, at a high level, transferring onto the stable
            manifold kind of undercuts the premise of using low thrust to reduce the
            transfer time
        \end{itshape}

        In this paper, the natural, uncontrolled dynamics represented by stable manifold are considered as a good starting point for low thrust orbital transfers, as orbital maneuvers with low thrust over a short time period would not differ from those substantially. 
        But, as pointed out by the reviewer, the proposed approach does not impose any optimality in the constructed maneuver. 
        The scope of this paper is constructing low thrust orbital maneuvers without relying on massive computations that appear in the common practice. 
        We aim to deliver a more systematic method for low thrust orbital design, which is to satisfy the given boundary conditions. 
        To clarify these, the revised manuscripts states that there is no optimality guaranteed.

@@

        The various reachable sets appear as straight lines due to the discretization used and the level of zoom of the figure.
        In reality the reachable sets are highly elongated ellipses on the \Poincare section.
        This is due to a combination of factors, namely that the low thrust propulsion cannot greatly deviate from the natural dynamics and that the nature of the optimization results in approximate numerical solutions subject to the choice of tolerance levels.
        In addition, as the figure shows there is a nontrivial relationship between terminal time and control magnitude. 
        The resulting reachability set is heaviliy dependent on the specific problem, choice of initial conditions, terminal time, and control bound.
        The figure is meant to illustrate some large scale, general properties of the approach, namely that an incrase in terminal time and/or control magnitude will have the effect of enlarging and moving the resulting reachable set.
     The intention is not to present an exhaustive search/discussion of this specific situation but rather to illustrate the effect of variations in terminal time and maximum control magnitude.
        The revised manuscript explicitly states this:
        \begin{correction}
            The reachable sets presented in~\cref{fig:varying_tf_reachability_sets} are highly dependent on the initial condition, terminal time, and maximum control bound. 
            This example demonstrates that increasing the \( u_m \) results in a larger displacement between the controlled and uncontrolled trajectories.
            The reachable set is enlarged from a single point, as shown in~\cref{fig:manifold_poincare} by the black point, to a larger region as shown in~\cref{fig:varying_tf_poincare}.
            The choice of \( u_m\), \( t_f \) and initial condition all combine to change the resulting reachability set. 
        \end{correction}
    \item
        \begin{itshape}

            * As mentioned before, the Poincare illustrations of Fig 2 and 3 would be
            more helpful if they were more general.  The first could benefit from
            showing nonperiodic dynamics, the second from showing a non-circular
            reachable boundary (I know the text acknowledges this but please update the
            figure).  
        \end{itshape}

        The illustrations of the \Poincare section match the typical depication in many other publications~\cite{koon2001}.
        Furthermore, the illustrations are merely utilized as helpful visualizations of the concepts, specifically periodic solutions, lower dimensional \Poincare sections, and reachable sets, rather than specific depictions of a solution.
        An additional comment is added to the caption specifically mentioning that the reachable set can be any arbitrary shape, and potentially non-continuous.

### 2018-09-04 Response.tex

        However, the example in Section 4.2 illustrates that the proposed approach can be linked together to compute low-thrust transfers for more challenging maneuvers, with the requirement of correcting energy error at the last stage. 
        This example demonstrates a possible approach to linking several computations of the reachability set to achieve a larger and more challenging transfer.
        There is still a difference in Jacobi energy which is corrected in the final stage.
        If needed in the multi stage examples, the Jacobi energy can be corrected in the intermediate steps to reduce the energy gap in the last stage.

        This paper is motivated by the current common practice of computing low thrust orbital transfers, where a large set of initial guess is repeatedly optimized in a computationally intensive manner. 
        The main contribution is presenting an alternative framework of constructing low thrust orbital transfers in a more efficient and systematic fashion. 
        The example in Section 4.2 demonstrates the use of several intersections of the reachability set to determine a transfer.

        In the revised manuscript, the following paragraph is added in Section 4.2 to explicitly describe the requirement of energy correction at the last stage, its implication and potential difficulties.

        \begin{correction}
            This numerical example demonstrates the ability to link several computations of the reachability set to enable a more general transfer.
            We use eight iterations of computing the reachability set in order to transfer from the geostationary orbit to the stable manifold.
            The example shows a transfer between an initial geostationary orbit and the stable manifold associated with a periodic orbit. 
            This approach allows for a larger class of potential transfers which leverage the capabilities of low-thrust propulsion systems.
            However, the presented approach does not offer a optimal solution in terms of energy/fuel usage. 
            The reachability sets are computed on the lower dimensional \Poincare section.
            As a result, the repeated intersections of the trajectory with the \Poincare section results in a fuel inefficient transfer.
            Furthermore, the issue of discrepancy in the Jacobi integral may become more serious when multiple reachability sets are interconnected. 
            Nonetheless, we are able to apply the proposed approach for the challenging case where the reachability set is not sufficiently close to the invariant manifold of the target orbit. 
            Consequently, this example illustrates a straightforward method to depart from the natural dynamics and transfer to a large region of the phase space that is not accessible via invariant manifolds alone.
            The presented idea of connecting reachability sets can be further studied to address the aforementioned issues of optimality and mismatch of the Jacobi integral.
        \end{correction}

### 2018-09-04 manuscript.tex
Update response with tylee edits

This numerical example demonstrates the ability to link several computations of the reachability set to enable a more general transfer.
We use eight iterations of computing the reachability set in order to transfer from the geostationary orbit to the stable manifold.
The example shows a transfer between an initial geostationary orbit and the stable manifold associated with a periodic orbit. 
This approach allows for a larger class of potential transfers which leverage the capabilities of low-thrust propulsion systems.
However, the presented approach does not offer a optimal solution in terms of energy/fuel usuage. 
The reachability sets are computed on the lower dimensional \Poincare section.
As a result, the repeated intersections of the trajectory with the \Poincare section results in a fuel inefficient transfer.
However, We are able to achieve a transfer that is not possible via the invariant manifold alone as manfiold does not pass sufficiently close to the Earth.
In addition, this example illustrates a straightforward method to depart from the natural dynamics and transfer to a large region of the phase space that is not accessible via invariant manifolds alone.

>>>>

This numerical example demonstrates the ability to link several computations of the reachability set to enable a more general transfer.
We use eight iterations of computing the reachability set in order to transfer from the geostationary orbit to the stable manifold.
The example shows a transfer between an initial geostationary orbit and the stable manifold associated with a periodic orbit. 
This approach allows for a larger class of potential transfers which leverage the capabilities of low-thrust propulsion systems.
However, the presented approach does not offer a optimal solution in terms of energy/fuel usage. 
The reachability sets are computed on the lower dimensional \Poincare section.
As a result, the repeated intersections of the trajectory with the \Poincare section results in a fuel inefficient transfer.
Furthermore, the issue of discrepancy in the Jacobi integral may become more serious when multiple reachability sets are interconnected. 
Nonetheless, we are able to apply the proposed approach for the challenging case where the reachability set is not sufficiently close to the invariant manifold of the target orbit. 
Consequently, this example illustrates a straightforward method to depart from the natural dynamics and transfer to a large region of the phase space that is not accessible via invariant manifolds alone.
The presented idea of connecting reachability sets can be further studied to address the aforementioned issues of optimality and mismatch of the Jacobi integral.
